Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-26 Paper/Manuscript.tex
Un peu plus sur x22

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[3]{Claire Labonne}
\author[1]{Anne Muller}
\author[4]{Céline Antonin}
\author[5]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr. The authors thank Marc Adam, Marcelo Olarreaga and anonymous referees for their comments and questions. Marc Adam pointed to us a slight data incoherence in Jacks \textit{et al.}'s .dta files that we have corrected in the following analysis.}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] { Paris School of Economics / Université Paris 1 Panthéon Sorbonne -- ACPR - Banque de France, 75009, PARIS, FRANCE}
\affil[4] {Sciences Po, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}
\affil[5] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE

@@

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially major result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs to the country and global level.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes \textit{a priori} changes in non-trade costs determinants of openness rates and hence can only rephrase the information contained in them.
\end{abstract}

@@

This is potentially an important result that sheds light on the globalization processes.
However, this result is actually driven by an \textit{ad hoc} method of aggregation that captures structure effects.
The authors use a weighted arithmetic average of bilateral transportation costs to compute country-specific trade costs. Putting aside the weight, in a simple symmetric three-country model, we show that this is the equivalent to using a power or generalized mean with exponent $1/(1-\sigma)$ on the value of dyadic trade flows\footnote{namely trade flows between a pair of countries} ($\sigma > 1$ is elasticity of substitution).
In contrast, a theoretically justified method would use a simple arithmetic mean of the value of the dyadic trade flow. 
Because $1/(1-\sigma)$ < 0, the importance of small dyadic trade flows in the computation of country-specific trade costs is too large in the authors' computations.
This is not compensated by the weight they use (end-of-period GDP).
Their conclusion on the difference between the two globalization periods comes from the fact that the dyads with the fastest growing trade in the first wave of globalization start with very small trade and this this is not the case in the second wave of globalization.

@@

\toprule
{1950-2000}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
Unweighted&355&4&284&-35&608 \tabularnewline
\textbf{GDP-weighted}&\textbf{350}&\textbf{6}&\textbf{230}&\textbf{-28}&\textbf{558} \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&350&3&318&-30&641 \tabularnewline
UK&297&11&227&-29&507 \tabularnewline
USA&341&9&180&-23&507 \tabularnewline
Average&350&6&224&-27&554 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&347&2&259&-21&587 \tabularnewline
UK&315&-12&219&-20&502 \tabularnewline
USA&342&10&161&-18&495 \tabularnewline
Average&347&9&184&-21&519 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&347&-1&317&-16&648 \tabularnewline
UK&347&-46&236&-15&522 \tabularnewline
USA&347&0&192&-13&526 \tabularnewline
Unweighted average&347&7&254&-16&592 \tabularnewline
\textbf{GDP-weighted average}&\textbf{347}&\textbf{2}&\textbf{203}&\textbf{-14}&\textbf{538} \tabularnewline
\bottomrule \addlinespace[1.5ex]

>>>>

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[3]{Claire Labonne}
\author[1]{Anne Muller}
\author[4]{Céline Antonin}
\author[5]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr. The authors thank Marc Adam, Marcelo Olarreaga and anonymous referees for their comments and questions. Marc Adam pointed to us a slight data incoherence in Jacks \textit{et al.}'s .dta files that we have corrected in the following analysis (and helped us with the programming). The authors are the sole responsible of mistakes in the text. Stata and tex files are available at https://github.com/gdaudin/GT\_ENSAE\_JMN.}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] { Paris School of Economics / Université Paris 1 Panthéon Sorbonne -- ACPR - Banque de France, 75009, PARIS, FRANCE}
\affil[4] {Sciences Po, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}
\affil[5] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE

@@

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially important result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs to the country and global level.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes a priori changes in non-trade costs determinants of openness rates and hence can only rephrases the information contained in them.
\end{abstract}

@@

This is potentially an important result that sheds light on the globalization processes.
However, that result is actually driven by an \textit{ad hoc} method of aggregation that captures structure effects.
The authors use an weighted arithmetic average of bilateral transport costs to compute country-specific trade costs. Putting aside the weight, in a simple symmetric three-country model, we show that this is the equivalent to using a power or generalized mean with exponent $1/(1-\sigma)$ on the value of dyadic trade flows ($\sigma > 1$ is elasticity of substitution).
In contrast, a theoretically justified method would use a simple arithmetic mean of the value of the dyadic trade flow. 
Because $1/(1-\sigma)$ < 0, the importance of small dyadic trade flows in the computation of country-specific trade costs is too large in the authors' computations.
This is not compensated by the weight they use (end-of-period GDP).
Their conclusion on the difference between the two globalization comes from the fact that the dyads with the fastest growing trade in the first wave of globalization start with very small trade and this this is not the case in the second wave of globalization.

@@

\toprule
{1950-2000}&{Contribution of growth in output}&{Contribution of growth in income similarity}&{Contribution of change in trade cost measure}&{Contribution of change in multilateral factors}&{Average growth of bilateral trade flows} \tabularnewline
\midrule\addlinespace[1.5ex]
&\multicolumn{5}{c}{JMN 2011} \tabularnewline
Unweighted&355&4&284&-35&608 \tabularnewline
\textbf{GDP-weighted}&\textbf{350}&\textbf{6}&\textbf{230}&\textbf{-28}&\textbf{558} \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, unweighted} \tabularnewline
FRA&350&3&318&-30&641 \tabularnewline
UK&297&11&227&-29&507 \tabularnewline
USA&341&9&180&-23&507 \tabularnewline
Average&350&6&224&-27&554 \tabularnewline
\midrule &\multicolumn{5}{c}{JMN by country, GDP-weighted} \tabularnewline
FRA&347&2&259&-21&587 \tabularnewline
UK&315&-12&219&-20&502 \tabularnewline
USA&342&10&161&-18&495 \tabularnewline
Average&347&9&184&-21&519 \tabularnewline
\midrule &\multicolumn{5}{c}{Our method} \tabularnewline
FRA&347&-1&318&-16&648 \tabularnewline
UK&347&-46&237&-15&522 \tabularnewline
USA&347&0&190&-11&526 \tabularnewline
Unweighted average&347&7&254&-15&592 \tabularnewline
\textbf{GDP-weighted average}&\textbf{347}&\textbf{2}&\textbf{202}&\textbf{-13}&\textbf{538} \tabularnewline
\bottomrule \addlinespace[1.5ex]
